Portal Forecast

### 2017-04-26 portal-forecast.Rmd

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('forecast-viz.R', echo = FALSE)
obs_data = PortalDataSummaries::abundance()
obs_data$total = rowSums(select(obs_data, -period))
new_moons = read.csv('~/PortalData/Rodents/moon_dates.csv')
obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "Period"))
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")

@@

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast-viz.R")
source("forecast_tools.R")
source("actual_census_counts.R")

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = PortalDataSummaries::abundance()
obs_data$total = rowSums(select(obs_data, -period))
new_moons = read.csv('~/PortalData/Rodents/moon_dates.csv')
obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "Period"))
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")

@@

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")
source("actual_census_counts.R")
